Tables/Graphs for Article

### 2017-12-22 article submission/draft1.Rnw
added citations

Questions analyzed were restricted to those posted in English. Time until event was defined as the time since posting until a question received its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date).

Survival was defined as the event that a question did not receive an answer beyond a certain time, t. Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored, or unanswered questions (cite). From these estimates, survival curves were constructed to examine the survival experience of questions. Mean, median and other percentiles of survival times were also generated.

As the probability distribution for answer times was unknown, a nonparametric Cox proportional hazards model was developed to predict survival probability (Cox models are not based on an assumption of the shape of the underlying probability distribution (cite)). To build the model, five-fold cross-validation was used. The full data was split into five training sets and five test sets. Univariate analysis, performed on one training set, was used to identify variables and transformations to potentially include in the final Cox model. Distributions of all continuous predictors, both with and without square root and log transformations, were assessed. Each categorical and continuous predictor, both untransformed and transformed, were entered into separate univariate Cox models, and strength of association with answer times were assessed. Those with partial likelihood ratio test p-values of less than 0.01 were included in the final model. For continuous predictors, the p-value was used to determine which form of the predictor to include---transformed or untransformed. To investigate the use of splines on continuous predictors, univariate analysis was again performed. Continuous variables (with transformations previously found to be necessary) were fit to four separate univariate Cox models with: restricted cubic splines of three, four, and five knots, and no splines. AIC statistics were used to determine whether or not splines were necessary, as well as the optimum number of knots \citep{Harrell2015}. All predictors found to be significant in both stages of univariate analysis were included in the model for cross-validation.

In each fold of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set. To assess prediction performance, the predicted hazard ratios were entered into separate Cox models as the single quantitative predictor, with answer times as the survival time. The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the model's performance \citep{Chen}. Signficant results would indicate high predictive accuracy. Concordance statistics and Somers' Dxy were also assessed to measure the model's predictive discrimination. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter survival time also has the higher predicted hazard. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' Dxy is the difference between the model's concordance statistic and discordance, 0.5 \citep{Harrell2015}. These metrics were computed for each iteration on every training and test set. Averages of metrics across test sets were evaluated. The final model was then fit to the full data and the same metrics were computed and compared.

Martingale residuals were evaluated to assess functional form of each continuous predictor. Deviance residuals were used to identify outliers, or questions poorly predicted by the model. Score residuals were used to identify questions that highly effected parameter estimates. Correlations between scaled Schoenfeld residuals, differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time. Significant correlations would indicate that a predictor has violated this assumption.

>>>>

Questions analyzed were restricted to those posted in English. Time until event was defined as the time since posting until a question received its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date) \citep{Kleinbaum2011}.

Survival was defined as the event that a question did not receive an answer beyond a certain time, t. Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored, or unanswered questions \citep{Bland1998}. From these estimates, survival curves were constructed to examine the survival experience of questions. Mean, median and other percentiles of survival times were also generated.

As the probability distribution for answer times was unknown, a nonparametric Cox proportional hazards model was developed to predict survival probability (Cox models are not based on an assumption of the shape of the underlying probability distribution) \citep{Moore2010}. To build the model, five-fold cross-validation was used. The full data was split into five training sets and five test sets \citep{sensitivity}. On one training set, distributions of all continuous variables were assessed and square root or log transformations were applied as necessary. Univariate analysis, performed on one training set, was used to identify variables to potentially include in the final Cox model \citep{Hammer}. Each categorical and continuous predictor was entered into separate univariate Cox models, and strength of association with answer times was assessed. Those with partial likelihood ratio test p-values of less than 0.001 were included in the final model. To investigate the use of splines on continuous predictors, univariate analysis was again performed. Continuous variables were fit to four separate univariate Cox models with: restricted cubic splines of three, four, and five knots, and no splines. AIC statistics were used to determine whether or not splines were necessary, as well as the optimum number of knots \citep{Harrell2015}. All predictors found to be significant in both stages of univariate analysis were included in the model for cross-validation. No variable selection was used, as \cite{Harrell2015} determined that reducing the number of predictors in the model harmed predictive accuracy, more so than leaving all predictors in.

In each fold of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set. To assess prediction performance, the predicted hazard ratios were entered into separate Cox models as the single quantitative predictor, with answer times as the survival time. The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the model's performance. Signficant results would indicate high predictive accuracy. Concordance statistics and Somers' Dxy were also assessed to measure the model's discriminative ability \citep{Chen}. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter survival time also has the higher predicted hazard. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' Dxy is the difference between the model's concordance statistic and discordance, 0.5. A Somers' Dxy statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \citep{Harrell2015}. These metrics were computed for each iteration on every training and test set. Averages of metrics across test sets were evaluated. The final model was then fit to the full data and the same metrics were computed and compared.

Correlations between scaled Schoenfeld residuals, differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time \citep{therneau}. Significant correlations would indicate that a predictor has violated this assumption .
